\textbf{Selective DNA and Protein Extraction from Marine Macrophyte Surfaces}

### 2019-10-21 submission/manuscript.tex
Chloroplast seq. selection optimization

\subsection{Abstract}\label{abstract}

@@

\subsection{Introduction}\label{introduction}

\subsection{Materials and Methods}\label{materials-and-methods}

\subsection{Results and Discussion}\label{results-and-discussion}

\subsection{Conclusions}\label{conclusions}

\subsection{Materials and Methods}\label{materials-and-methods-1}

@@

\subsection{References}\label{references}

>>>>

\hypertarget{abstract}{%
\subsection{Abstract}\label{abstract}}

@@

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

\#\#Materials and Methods

\hypertarget{results-and-discussion}{%
\subsection{Results and Discussion}\label{results-and-discussion}}

\hypertarget{conclusions}{%
\subsection{Conclusions}\label{conclusions}}

\hypertarget{materials-and-methods}{%
\subsection{Materials and Methods}\label{materials-and-methods}}

@@

\hypertarget{references}{%
\subsection{References}\label{references}}
